On FX Rates and a Multivariate GARCH model

### 2016-10-05 papers/FX/fx.tex
Some revision to the FX project and some to the GARCH(p,q) project.

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.3]{FX_eigenvectors}  
  \caption{FX \& ARCH eigenvectors}
  \label{fig:FX_ARCH_eigenvectors}
\end{figure}

\section{General IGARCH(1)}
For general IGARCH(1) models, the equation
\begin{equation*}
  \E \left[
    (
    \alpha_{i,1} Z_1^2 + 1 - \alpha_{i,1}
    )^\xi
    (
    \alpha_{j,1} Z_2^2 + 1 - \alpha_{j,1}
    )^\xi\right] = 1
\end{equation*}
has to be solved numerically. Figure \ref{fig:xi_rho0.5} shows $\xi$
as a function of $(\alpha_{i,1}, \alpha_{j,1})$ as defined by the
above equation.
\begin{figure}[htb!]
  \centering
  % \includegraphics[scale=0.4]{igarch_rho0dot5.pdf}
  \caption{$\xi(\alpha_1, \alpha_2)$ for $\rho = 1/2$}
  \label{fig:xi_rho0.5}
\end{figure}

\section{Spectra of S\&P sectors}
\subsection{Utilities}
Fitting the daily returns' data of 25 companies that have been
included in the S\&P 500 index since 2010-01-01 and categorized in the
sector ``Utilities'', we obtained 23 GARCH(1, 1) models that satisfy
the condition
\begin{equation}
  \label{eq:garch_cond1}
  \alpha_1 + \beta_1 < 1  
\end{equation}
Then we simulate the GARCH(1, 1) processes with innovations having the
same covariance structure as those of the real data. Figure
\ref{fig:Utilities_eigenvalues} and \ref{fig:Utilities_eigenvectors1},
\ref{fig:Utilities_eigenvectors2}
compare the eigenvalues and eigenvectors, respectively, of the 
covariance matrices of the real and the simulated data.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.6]{Utilities_eigenvalues.pdf}
  \caption{Eigenvalues of Utilities: real \& simulated}
  \label{fig:Utilities_eigenvalues}
\end{figure}

>>>>

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.3]{FX_eigenvectors.pdf}  
  \caption{FX \& ARCH eigenvectors}
  \label{fig:FX_ARCH_eigenvectors}
\end{figure}

\section{General IGARCH(1)}
For general IGARCH(1) models, the equation
\begin{equation*}
  \E \left[
    (
    \alpha_{i,1} Z_1^2 + 1 - \alpha_{i,1}
    )^\xi
    (
    \alpha_{j,1} Z_2^2 + 1 - \alpha_{j,1}
    )^\xi\right] = 1
\end{equation*}
has to be solved numerically. Figure \ref{fig:xi_rho0.5} shows $\xi$
as a function of $(\alpha_{i,1}, \alpha_{j,1})$ as defined by the
above equation.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.4]{igarch_rho0dot5.pdf}
  \caption{$\xi(\alpha_1, \alpha_2)$ for $\rho = 1/2$}
  \label{fig:xi_rho0.5}
\end{figure}

\section{Heavy-Tailed Innovations}
Figure \ref{fig:ARCH_t_FX_eigenvalues} and Figure
\ref{fig:ARCH_t_FX_eigenvectors} show the eigenvalues and
eigenvectors of the simulated GARCH(1, 1) process with innovations
following t(4) distribution. Clearly, the spectrum of the simulated
series does not match that of the observed FX series.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.4]{FX_eigenvalues_ARCH_t_inno.pdf}  
  \caption{FX \& simulated ARCH eigenvalues. t-distributed innovations}
  \label{fig:ARCH_t_FX_eigenvalues}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.3]{FX_eigenvectors_ARCH_t_inno.pdf}  
  \caption{FX \& ARCH eigenvectors. t-distributed innovations}
  \label{fig:ARCH_t_FX_eigenvectors}
\end{figure}

\section{Spectra of S\&P sectors}
\subsection{Utilities}
Fitting the daily returns' data of 25 companies that have been
included in the S\&P 500 index since 2010-01-01 and categorized in the
sector ``Utilities'', we obtained 23 GARCH(1, 1) models that satisfy
the condition
\begin{equation}
  \label{eq:garch_cond1}
  \alpha_1 + \beta_1 < 1  
\end{equation}
Then we simulate the GARCH(1, 1) processes with innovations having the
same covariance structure as those of the real data. Figure
\ref{fig:Utilities_eigenvalues} and \ref{fig:Utilities_eigenvectors1},
\ref{fig:Utilities_eigenvectors2}
compare the eigenvalues and eigenvectors, respectively, of the 
covariance matrices of the real and the simulated data.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.4]{Utilities_eigenvalues.pdf}
  \caption{Eigenvalues of Utilities: real \& simulated}
  \label{fig:Utilities_eigenvalues}
\end{figure}
